Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-05-15 cthpc-2017/paper.tex
Fix grammar errors
Move the lane detector performace to the right place
Wording tweaks

The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in Figure \ref{fig:overall_arch}. It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then feeds back to the cars to increase their mapping and localization effectiveness.

@@

Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.

@@

Our basic setup was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.

@@

The camera was calibrated before activating the controller. Two parameters are used to describe the relationship between image and real world: intrinsic matrix and extrinsic matrix.

@@

The extrinsic matrix represents the rotation and translation of camera with respect to the world. A linear transformation called Homograpy is applied on  the matrix to change the camera view purely mathematically.

@@

\begin{table}[!htbp]
	\centering
	\caption{Lane detector performance and test conditions}
	\label{lane_detector_condition}
	\begin{tabular}{ll}
		Frame rate                      &10fps \\
		Image format                    &8-bits RGB cv::Mat \\
		Image size                      &320x240 px	 \\	
		ROI (Region of Interest) size   &320x120 px
	\end{tabular}
\end{table}

>>>>

Various hardware components e.g., sensors, motors, wireless devices, and ARM SoC are used for a self-driving miniature vehicle. When selecting the cost-efficient components, the general
selection criteria were efficiency, low-power consumption, low-price, availability and extendability.

The system allows the existence of multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in Figure \ref{fig:overall_arch}. It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then reacts to the cars to increase their mapping and localization effectiveness.

@@

Despite limited the budget shown in Table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car interaction and route planning.

@@

Our basic configuration was inspired by MIT Duckietown \cite{Duckietown}, and we created an artificial environment where the lane detector can be implemented in straightfoward ways. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.

@@

The camera was calibrated before we activated the controller. Two parameters are used to describe the relationship between image and real world: intrinsic matrix and extrinsic matrix.

@@

The extrinsic matrix represents the rotation and translation of camera with respect to the world. A linear transformation called Homograpy is applied to the matrix, changing the camera view purely mathematically.

@@

\begin{table}[!htbp]
	\centering
	\caption{Lane detector performance and test conditions}
	\label{lane_detector_condition}
	\begin{tabular}{ll}
		Frame rate                      &10fps \\
		Image format                    &8-bits RGB cv::Mat \\
		Image size                      &320x240 px	 \\	
		ROI size                        &320x120 px
	\end{tabular}
\end{table}
